Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
swapping sections
rewording in related works

The model is related to online
caching~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}. In our
setting, requests can be served remotely, which is
reminiscent of caching models \emph{with
bypassing}~\cite{EpImLN11,EpImLN15,Irani02}.

@@

\subsection{The Perfect Partition Variant}	\label{sec:PP}
In Section \ref{sec:ppl},
we give an algorithm for a restricted variant of  \OBRP{},
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to ``recover" (or learn) the perfect partition while not paying too much more than OPT.
This implies that on a request between any two non-collocated nodes,
any online algorithm must eventually collocate them,
as otherwise it not competitive under a sequence that repeats the same request arbitrarily many times.
Hence,
any competitive algorithm,
must at some point collocate all nodes of a  connected sub-graph of the communication graph.
We refer to this connected sub-graph as a \emph{component}.
An algorithm that always keeps a component collocated is \emph{component-respecting}.

@@

The gap between upper and lower bound is still substantial, as the best known algorithm is the component-based algorithm of   \cite{repartition-disc} with competitive ratio $O(k^2\cdot\ell^2)$.

>>>>

%The model is related to online
%paging~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}.
In our
setting,
each  requests between two nodes  not in the same cluster
(i.e., inter-cluster requests) inflicts a cost until the nodes are placed in the same cluster.
This is a reminiscent of caching models \emph{with
rejection} penalty~\cite{EpImLN11,EpImLN15,Irani02}.

@@

\subsection{The Perfect Partition Variant}	\label{sec:PP}
In Section \ref{sec:ppl},
we give an algorithm for a restricted variant of  \OBRP{},
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to ``recover" (or learn) the perfect partition while not paying too much more than OPT.
This implies that on a request between any two non-collocated nodes,
any online algorithm must eventually collocate them,
as otherwise it not competitive under a sequence that repeats the same request arbitrarily many times.
Hence,
any competitive algorithm,
must at some point collocate all nodes of a  connected sub-graph of the communication graph.
We refer to this connected sub-graph as a \emph{component}.
An algorithm that  keeps all components collocated is \emph{component-respecting}.

@@

The gap between upper and lower bound is still substantial, as the best known algorithm is the component-respecting algorithm of   \cite{repartition-disc} with competitive ratio $O(k^2\cdot\ell^2)$.
